Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data

### 2017-01-05 Inelastic/analysis.tex
bkg model written

\subsection {Background Model}
Description of the data driven bkg model evaluation, few numbers on estimated background, words about cross checks with Th232.

%A citation in text uses the command \verb+\cite{#1}+ or
%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
%An entry in the bibliography is a reference to another document.
\subsection{Systematic Uncertainties}

few words, mainly a table summarizing uncertainties.

>>>>

\subsection {Background Model}

The expected background in the region of interest is mainly caused by material radioactivity, mainly photons that 
interact via compton scattering, background due to activation of Xe 39.6 line from radiogenic neutrons is found to be negligible.
To model this background we use data from $^{60}$Co calibration campaign, the assumption is
that the $^{60}$Co data are representative of the density in cS1-cS2 plane of the background. The calibration sample events
in the ROI amount to  22225 events, this yield is then scaled to data according to a measured background scale factor $\tau_{bkg}$.

The scale factor is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2, the two control 
regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
is of statistical nature only.

The distribution of the calibration sample has been compared to the data of the sience run in the two control regions,
agreement is found within statistical uncertainties. $^{60}$Co calibration data have been compared in the region of interest to  
data from $^{232}$Th calibration campaign, the largest deviation between the two shapes is within 4\%. An additional systematic
uncertainty of 4\% has been applied to the expected background yield of each subregion of the ROI.

\subsection{Systematic Uncertainties}

few words, mainly a table summarizing uncertainties. Figure~\ref{fig:unc}.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
  \caption{Signal region, uncertainties for WIMP of mass 100~GeV.}
  \label{fig:unc}
\end{figure}
